---
title: 'C&S 311'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
# For this assignment I consult with Hao Shen.
# I made the explain and parts of looping by myself. However,I got lost and trouble when I try to figure out the logic of looping. I learned the logic from my classmates.

```



## Research on the logic

```{r}
n = 100
m = c(50, 60, 70, 80, 90)
p = seq(0.4, 1, 0.01)

for (i in m) {
  if (i == m[1]) {
    Total = data.frame(p, effective=as.character(i),result=cumsum(dbinom(i,n,p)))
  }
  else {
     Total = rbind( Total, data.frame(p, effective=as.character(i), result=cumsum(dbinom(i,n,p))))
  }
}


ggplot()+
  geom_rect(aes(xmin = 0.6, xmax = 0.8, ymin = 0.05, ymax = 0.95))+
  geom_line(aes(p, result, color = effective), Total)



```
With total 100 sample size, the larger m will move the curve to further right.  5% type 1 error is shown by the bottom line and (1-95%) type 2 error is represented by top line .we need to find the line with smallest m cross the bottom of the box and the line with largest m cross with the top of the box. 

## Redo and explain

```{r}
n = 100
m = c(69,73)
p = seq(0.4, 1, 0.01)
for (i in m) {
  if (i == m[1]) {
    Total = data.frame(p, effective=as.character(i),result=cumsum(dbinom(i,n,p)))
  }
  else {
     Total = rbind( Total, data.frame(p, effective=as.character(i), result=cumsum(dbinom(i,n,p))))
  }
  
}
ggplot()+
  geom_rect(aes(xmin = 0.6, xmax = 0.8, ymin = 0.05, ymax = 0.95))+
  geom_line(aes(p, result, color = effective),  Total)
  
```

 Finding the line (red) with smallest m=69 cross the bottom of the box and the line(blue) with largest m=73 across with the top of the box. Therefor m between 69 and 73 is reliable.
